Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2016-11-10 Presentation/gpm_november2016_vianello.tex
after crash bare stikord

\documentclass[10pt, compress]{beamer}
\usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

@@

>>>>

\documentclass[10pt, compress, draft]{beamer}
\usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

@@

\section{Topic 21 experiments }
\begin{frame}{more proposed shots than allocated}
	\begin{itemize}
		\item totla number propose shots 449
		\item ebven though combined we have to prioritize
		\item prioritize cross comparison 
		\item 
	\end{itemize}
\end{frame}

\begin{frame}{Focal points}
	Hmode (Proponentrs)
	L-mode :  neutrals Ip scan
\end{frame}

\begin{frame}{requirements form cross machine comparison }
same configuration, SN Btimes grad b, cryo pumps, greenwald fraction, heating

same diagnostics Isat blob speed, density profiles (Libes reflectometry), , divertor n and Te, fast camera plus n and te measure at OM

status of cameras on devices
